\documentclass[11pt]{article}

\usepackage[letterpaper, margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{booktabs}
\usepackage{parskip}
\usepackage{tabularx}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}

% Helper for rough-draft notes and questions
\newcommand{\todo}[1]{\textcolor{red}{\textbf{[TODO: #1]}}}
\newcommand{\note}[1]{\textcolor{blue}{\textit{[NOTE: #1]}}}
\newcommand{\question}[1]{\textcolor{magenta}{\textbf{[QUESTION: #1]}}}

\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{1em}{}

\title{
    \vspace{-1in}
    \textbf{Universal Plastic Shredder V2.0}\\
    \large Electrical Control and Power System\\
    \normalsize \textbf{Final Report - Rough Draft}
}
\author{
    Team 07: I'm So Shredded INC\\
    Bao Nguyen, Fearghus Tyler, Yaqoub Rabiah, Fox Kang\\
    \texttt{baon@pdx.edu, fearghus@pdx.edu, yrabiah@pdx.edu, foxkang@pdx.edu}\\[4pt]
    Industry Sponsor: MME / Ichor Systems (Bridget Lannigan)\\
    Faculty Advisors: Prof. Andrew Greenberg, Dr. Jonathan Bird (EE), Robert Paxton (ME)\\[4pt]
    ECE 412 Senior Project Development I/II\\
    Portland State University, Winter--Spring 2026
}
\date{Rough Draft Submission: May 31, 2026}

\begin{document}
\maketitle
\thispagestyle{empty}

\noindent\rule{\textwidth}{0.4pt}
\note{This is a rough draft. Sections marked TODO, NOTE, or QUESTION indicate areas where we need to expand content, gather data, or get advisor input before the final submission. Bullet points are placeholders for fuller prose in the final version.}
\noindent\rule{\textwidth}{0.4pt}

\tableofcontents
\newpage

\section{Executive Summary}

\begin{itemize}
    \item Ichor Systems generates significant plastic waste (PVC, polypropylene, LDPE) during semiconductor equipment manufacturing, currently sent to landfill.
    \item Commercial industrial shredders cost \$10,000+ and consumer units cannot handle the thick rigid sheets (0.25--0.5 in).
    \item Our project designs the electrical control and power system for a custom industrial-grade plastic shredder, capable of shredding into 1-inch pieces.
    \item Key elements: VFD-controlled 3 HP motor at 70--90 RPM output, two-hand safety control, lid interlock, E-stop, jam-detection auto-recovery with 3-strike lockout, NEMA-enclosed PLC and HMI.
    \item Total budget: \$3,000 (EE portion approximately \$1,000).
\end{itemize}

\question{Should the executive summary include high-level results / status (e.g., ``shredder validated to X HP load with Y throughput rate'') once we complete testing? Currently we have signal-chain validation but not full mechanical load testing.}

\section{Introduction}

\subsection{Background and Motivation}
\begin{itemize}
    \item Ichor Systems is a Portland-area semiconductor equipment manufacturer.
    \item Their manufacturing processes produce substantial volumes of rigid plastic sheet waste.
    \item Existing disposal route: landfill -- environmentally and economically suboptimal.
    \item A previous 2023--2024 PSU capstone team built a 2 HP household shredder for the EPL. This project scales to industrial-grade.
\end{itemize}

\subsection{Project Scope}
\begin{itemize}
    \item EE team responsibility: motor control, safety circuits, PLC logic, HMI, power distribution.
    \item ME team (separate) handles mechanical frame, blade assembly, gearbox.
    \item Integration plan: mechanical structure delivered with motor mount; EE team commissions controls.
\end{itemize}

\todo{Add a one-paragraph background on dynamic recycling / circular economy framing for the introduction.}

\section{Requirements}

\subsection{Must-Have}
\begin{itemize}
    \item Shred 0.25--0.5 in plastic sheet into approximately 1-inch pieces.
    \item Controllable VFD supporting 3--5 HP motor at 70--90 RPM output shaft speed.
    \item Follow NFPA 70 (NEC) electrical design guidance.
    \item Include emergency stop, overcurrent/overload protection, at least one safety interlock.
    \item Include an HMI for operator control and status display.
    \item Stay within \$3,000 total project budget.
\end{itemize}

\subsection{Should-Have}
\begin{itemize}
    \item Clear status and fault indicator lights.
    \item Follow NEMA enclosure guidelines.
    \item Clearly labeled controls.
\end{itemize}

\subsection{May-Have (if time/budget allow)}
\begin{itemize}
    \item Wireless monitoring (read-only).
    \item Data logging of operating hours and faults.
    \item Additional safety sensing (capacitive touch, thermal).
\end{itemize}

\section{System Architecture}

\subsection{Hardware Subsystems}
\begin{itemize}
    \item \textbf{AC power input:} 120 VAC mains $\rightarrow$ main disconnect $\rightarrow$ branch breakers $\rightarrow$ VFD and 24V PSU.
    \item \textbf{VFD:} Huanyang HY02D211B-T (2.2 kW, 110V single-phase input, 220V 3-phase output boost-type). Controlled via FOR/REV/RST digital inputs.
    \item \textbf{Motor:} GE 5KE182BC205B, 3 HP, 230V (low-voltage connection), 1750 RPM, FLA 7.6 A.
    \item \textbf{Brake resistor:} 75 $\Omega$, 500 W, connected to VFD's P/Pr terminals to handle regenerative energy during deceleration and reversal.
    \item \textbf{PLC:} AutomationDirect H2-DM1E (Do-more CPU) on DL205 base, D2-08ND3 discrete input module.
    \item \textbf{HMI:} AutomationDirect C-more Micro-Graphic EA1-T4CL 4-inch color touch panel, connected to the H2-DM1E CPU serial communication port (operator commands to the PLC; status/data back to the panel). Powered from the shared Mean Well NDR-480-24 24\,VDC supply.
    \item \textbf{Safety circuit:} Hardwired E-stop loop, lid interlock, two-hand deadman start. Motor contactor energized through safety chain.
    \item \textbf{24V DC supply:} Mean Well NDR-480-24 (480 W) for control voltage.
\end{itemize}

\subsection{Signal Flow}
\begin{itemize}
    \item Operator inputs (deadman buttons, E-stop, reset, lid interlock) $\rightarrow$ PLC discrete inputs (D2-08ND3, sourcing mode).
    \item PLC outputs (D2-08TR relay module, common to PSU --V) $\rightarrow$ VFD FOR (Y7), REV (Y6), RST (Y5) inputs in sinking (NPN) mode.
    \item VFD fault relay (FC + FA, NO active-high) $\rightarrow$ PLC X5 input. X5 = HIGH when VFD trips on fault, LOW when healthy.
    \item HMI $\leftrightarrow$ PLC via serial (H2-DM1E CPU serial COM port; matched baud, parity, and stop bits on both ends).
\end{itemize}

\todo{Insert system block diagram here. Convert one of the AutoCAD drawings or draw fresh in draw.io.}

\section{Hardware Design}

\subsection{Power Distribution}
\begin{itemize}
    \item Main disconnect: \todo{specify rating}.
    \item VFD branch breaker: 30 A C-curve DIN-rail (handles inrush, sized per NEC 430.52).
    \item 24V PSU branch breaker: 10 A C-curve DIN-rail.
    \item \textbf{Conductors:} power runs use 12 AWG copper (THHN/MTW), rated 20 A / 25 A / 30 A at the 60/75/90\,\textdegree C ampacity columns of NEC Table 310.16 -- well above the motor's 7.6 A FLA and the VFD input current. Control wiring uses 16--18 AWG, ferruled at all terminal blocks.
    \item \textbf{Fuse / OCPD sizing:} branch and component fuses are sized at \textbf{125\% of the protected component's rated continuous load} per NEC 210.20(A) / 215.3. (The motor branch breaker is the exception -- NEC 430.52 permits a higher multiple of FLC to ride through inrush; running overload is handled by the VFD's electronic motor-overload function.)
    \item All branches fused individually at terminal blocks for downstream loads.
\end{itemize}

\subsection{Motor and VFD}
\begin{itemize}
    \item Selected Huanyang HY02D211B-T over alternatives via decision matrix (price, documentation, reliability).
    \item Programmed motor parameters: \texttt{PD141 = 230 V}, \texttt{PD142 = 7.6 A}, \texttt{PD143 = 4 poles}, \texttt{PD144 = 1750 RPM}.
    \item Over-torque detection programmed: \texttt{PD052 = 02} (fault indication on relay), \texttt{PD123 = 3}, \texttt{PD124 = 150} (\%), \texttt{PD125 = 3.0 s}.
    \item Brake resistor connected to P/Pr terminals to handle regenerative energy from rapid reversal during jam-clear cycles.
\end{itemize}

\note{The over-torque relay function (\texttt{PD052 = 12}) did not fire the relay in our specific Huanyang revision when \texttt{PD123 = 2} (continue running). Documented as a firmware-specific limitation (see the VFD parameter table, Appendix D). Working configuration uses \texttt{PD052 = 02} (fault indication) and \texttt{PD123 = 3} (over-torque triggers self-trip, which fires the fault relay). The PLC then runs the unjam routine including a RST pulse to clear the VFD's latched fault state between retry attempts.}

\subsection{Safety Circuit}
\begin{itemize}
    \item E-stop: NC contact pair in hardwired loop. Drops motor contactor on activation.
    \item Lid interlock: NC switch in same hardwired safety loop.
    \item Two-hand deadman: both buttons must be held continuously to enable motor.
    \item Motor contactor: K1 main contactor energized through safety chain. PLC outputs RUN command \emph{through} the contactor, so safety chain has hardware precedence over PLC.
\end{itemize}

\todo{Add safety circuit schematic. Reference NFPA 79 section 9 for safety-related stop functions.}

\subsection{Jam Detection Signal Chain}
\begin{itemize}
    \item VFD's multi-function relay (terminals FA, FB, FC) programmed for Fault Indication (\texttt{PD052 = 02}). \textbf{Only FA and FC are used} for jam detection; the FB (normally-closed) contact is left unconnected.
    \item Wired as an NO active-high pair: +24V (through a 500 mA fast-blow fuse) feeds the FA contact; the FC common returns to PLC X5 input on D2-08ND3 (Slot 2). When the VFD trips, FA--FC closes and +24V reaches X5.
    \item PLC sees X5 = LOW during normal operation, X5 = HIGH when VFD trips on any fault (over-torque, overvoltage, overheat, etc.).
    \item PLC ladder reads \texttt{[ X5 ]} on rising edge to detect new fault events.
    \item Wire-break failure mode is handled at the safety-circuit level by the redundant hardwired E-stop loop and motor contactor, rather than at the jam-signal level.
    \item Full terminal-by-terminal wiring is given in the I/O point list (Appendix B) and the VFD parameter/wiring table (Appendix D).
\end{itemize}

\section{Software Design}

\subsection{PLC Ladder Logic Architecture}
\begin{itemize}
    \item Do-more Designer stage program (similar to grafcet / SFC).
    \item States: IDLE, RUNNING, JAM\_DETECTED, RST\_PULSE, REVERSE, RESUME, LOCKOUT.
    \item Transitions driven by deadman input, X5 jam signal, jam counter, and reset button.
\end{itemize}

\subsection{State Machine}
\begin{itemize}
    \item \textbf{IDLE} $\rightarrow$ RUNNING when both deadman buttons held AND not locked out AND startup mask done.
    \item \textbf{RUNNING} $\rightarrow$ JAM\_DETECTED on rising edge of X5 (VFD trip → fault relay fires → X5 goes HIGH).
    \item \textbf{JAM\_DETECTED} $\rightarrow$ RST\_PULSE if jam count $< 3$, $\rightarrow$ LOCKOUT if jam count $\geq 3$.
    \item \textbf{RST\_PULSE} (500 ms) $\rightarrow$ REVERSE (2 s).
    \item \textbf{REVERSE} $\rightarrow$ RESUME (brief delay) $\rightarrow$ back to RUNNING.
    \item \textbf{LOCKOUT} $\rightarrow$ IDLE only via dedicated reset button.
\end{itemize}

\subsection{Jam Counter Reset Logic}
\begin{itemize}
    \item Counter increments on each X5 rising edge (each new VFD fault triggers a jam event).
    \item Resets to 0 if motor runs cleanly for 30 continuous seconds in the RUNNING state.
    \item Also resets if deadman is released for 30 continuous seconds (session reset).
    \item Whichever condition fires first wins.
\end{itemize}

\subsection{Startup Mask}
\begin{itemize}
    \item For first 5 seconds after PLC power-up, X5 is ignored.
    \item In NO active-high wiring, this guards against transient X5 pulses during VFD initialization. Less critical than under NC wiring but kept as a defensive measure.
\end{itemize}

\subsection{HMI Programming}
\begin{itemize}
    \item Status displays: Ready, Running, Jam in progress, Lockout, Fault.
    \item Operator inputs: Speed setpoint (currently fixed in PLC), Reset button.
    \item Data displayed: Motor current (read from VFD over Modbus -- \todo{verify Modbus setup}), Jam count this session, Total runtime.
\end{itemize}

\question{We have not finalized the HMI screen layout. Should we include mock-ups in the rough draft, or wait for the final?}

\section{Safety Design}

\subsection{NFPA 79 Compliance}
\begin{itemize}
    \item Wire color coding follows NFPA 79 §13.2: Black for AC line/load, Red for AC control, Blue for DC control, Blue/W stripe for DC return, Green/Yellow for ground.
    \item This color convention is applied to every conductor in the panel.
    \item All control wires labeled at both ends.
    \item All control wires terminated with crimped ferrules at terminal blocks.
\end{itemize}

\subsection{Hardwired Safety Functions}
\begin{itemize}
    \item E-stop: Category 0 stop (immediate removal of power) per ISO 13849. NC fail-safe wiring.
    \item Lid interlock: NC fail-safe; opens motor contactor when lid raised.
    \item Two-hand control: per ISO 13851 (Type IIIA at minimum) -- buttons must be pressed within 0.5 s of each other and held continuously.
    \item Overload: motor thermal protection in VFD plus separate motor contactor with overload relay.
\end{itemize}

\todo{Confirm we are meeting Category 1 or higher per ISO 13849-1. Need to walk through the SIL/PL calculation or get a hand-wave from the advisor that capstone scope doesn't require formal SIL.}

\subsection{Failure Mode Analysis}
\begin{itemize}
    \item Wire break in jam signal: PLC sees X5 stuck LOW. Jam signal cannot fire, but the hardwired E-stop loop and motor contactor provide independent safety. Operator can also see motor stop and trigger investigation via fault-light absence.
    \item VFD loses power: the FA--FC fault relay de-energizes and opens, so X5 reads LOW (indistinguishable from healthy). The motor stops because the VFD itself is unpowered, so the condition is caught by the motor not running rather than by the jam signal.
    \item PLC fails: motor contactor drops out (safety chain bypasses PLC). Motor coasts to stop.
    \item Brake resistor disconnected: VFD will trip on overvoltage during deceleration. Motor coasts to stop. Diagnosable from VFD display.
\end{itemize}

\section{Standards and Regulatory Compliance}

This section consolidates every electrical and machine-safety standard the design
is built against and states, for each, how it is applied to the shredder. Many of
these are referenced in passing elsewhere in this report; they are gathered here so
a reviewer (or a future maintenance team) can audit compliance in one place.

\subsection{Standards Summary Matrix}

\renewcommand{\arraystretch}{1.3}
\noindent\begin{tabularx}{\textwidth}{@{}l l X@{}}
\toprule
\textbf{Standard} & \textbf{Scope} & \textbf{How it is applied here} \\
\midrule
NFPA 70 (NEC) & National Electrical Code -- premises wiring, motor circuits & Branch-circuit, conductor, grounding, and disconnect design (see \S\ref{subsec:nec}). \\
NFPA 79 & Electrical standard for industrial machinery & Wire color coding, supply disconnect, protective bonding, stop functions, operator devices (see \S\ref{subsec:nfpa79}). \\
NEMA 250 & Enclosure type ratings & Control enclosure selected to a NEMA type matched to the lab/shop environment (see \S\ref{subsec:nema}). \\
NEMA ICS 1/2 & Industrial control \& systems & Contactor / control device selection and marking. \\
NEMA MG 1 & Motors and generators & Motor nameplate interpretation and VFD parameterization. \\
UL 508A & Industrial control panels & Panel construction practice and short-circuit current rating (SCCR) awareness. \\
IEC 60204-1 & Safety of machinery -- electrical equipment & International counterpart to NFPA 79; used to cross-check stop categories. \\
ISO 12100 & Risk assessment / risk reduction & Framework behind the hazard analysis driving the safety circuit. \\
ISO 13849-1 & Safety-related parts of control systems (PL) & Target performance level for E-stop / interlock chain. \\
ISO 13850 & Emergency stop function & E-stop actuator type, color, and Category 0 behavior. \\
ISO 13851 & Two-hand control devices & Deadman two-hand start timing and configuration. \\
OSHA 29 CFR 1910.147 & Lockout/Tagout (LOTO) & Lockable main disconnect for energy isolation during service. \\
\bottomrule
\end{tabularx}
\renewcommand{\arraystretch}{1.0}

\subsection{NFPA 70 -- National Electrical Code}
\label{subsec:nec}
\begin{itemize}
    \item \textbf{Article 430 (Motors, Motor Circuits, and Controllers)} -- the governing article for this build.
    \begin{itemize}
        \item \texttt{430.6}: motor full-load current taken from the nameplate / NEC tables (GE 5KE182BC205B, FLA 7.6 A at 230 V) as the basis for all downstream sizing.
        \item \texttt{430.22}: branch-circuit conductors sized at $\geq 125\%$ of motor FLC.
        \item \texttt{430.32}: running overload protection -- provided by the VFD's electronic motor-overload function (programmed motor FLA \texttt{PD142 = 7.6 A}) plus over-torque trip.
        \item \texttt{430.52}: branch-circuit short-circuit / ground-fault protection -- 30 A C-curve breaker on the VFD branch, sized to clear inrush without nuisance trips (within the inverse-time-breaker allowance).
        \item \texttt{430.102} / \texttt{430.109}: a disconnecting means is provided ahead of the controller and VFD.
        \item \textbf{Part X (Adjustable-Speed Drive Systems, \texttt{430.122})}: conductor and protection rules applied to the VFD-fed motor circuit.
    \end{itemize}
    \item \textbf{Article 250 (Grounding and Bonding):} equipment grounding conductor (green / green-yellow) bonds the VFD chassis, PSU chassis, motor frame, and panel to a common ground bus and building earth.
    \item \textbf{Article 310 (Conductor Ampacity):} control and power conductors selected from the ampacity tables for the installed temperature rating.
    \item \textbf{Article 409 (Industrial Control Panels):} panel layout, marking, and overcurrent considerations.
    \item \textbf{Article 110.26 (Working Space):} clearances around live parts maintained for safe service access. \todo{Confirm final panel mounting leaves required working clearance.}
\end{itemize}

\note{As-built deviation flagged during the Point List review: the SD-N35 safety
contactor switches the VFD \emph{neutral} (T) leg rather than the \emph{hot} (R) leg.
NEC / NFPA 79 practice is to switch the ungrounded (hot) conductor so that opening the
contactor de-energizes the load to ground potential. Switching the grounded conductor
leaves the load at line potential when the contactor is open. This is documented in
the as-built I/O point list (Appendix B, VFD terminals) and must be corrected, or
explicitly justified and risk-assessed, before final sign-off.}

\subsection{NFPA 79 -- Electrical Standard for Industrial Machinery}
\label{subsec:nfpa79}
\begin{itemize}
    \item \textbf{\S5.3 Supply circuit disconnecting means:} a lockable main disconnect isolates the machine from the supply (also satisfies LOTO, below).
    \item \textbf{\S7 Overcurrent protection:} individual branch and downstream-load fusing at the terminal blocks (PSU branch 25 A slow-blow, PLC branch 1 A fast-blow, control loads individually fused).
    \item \textbf{\S8 Protective bonding circuit:} continuous equipment-grounding/bonding path to all exposed conductive parts.
    \item \textbf{\S9 Control circuits and functions:} stop functions classified by stop category (see safety section); the hardwired safety chain has precedence over the PLC.
    \item \textbf{\S10.7--10.8 Operator interface / emergency stop:} E-stop uses a red mushroom actuator on a yellow background with a self-latching NC contact; start devices are guarded against accidental operation by the two-hand requirement.
    \item \textbf{\S13.2 Conductor identification (color coding):} black = AC line/load, red = AC control, blue = DC control, blue/white = grounded (return) DC, green/yellow = protective earth. All control wires are labeled at both ends and terminated with crimped ferrules.
\end{itemize}

\subsection{NEMA Standards}
\label{subsec:nema}
\begin{itemize}
    \item \textbf{NEMA 250 (Enclosures):} the control enclosure is selected to a NEMA type appropriate for a dry indoor shop/lab with airborne plastic dust -- targeting NEMA Type 12 (dust-tight, drip-tight) for the PLC/HMI panel. \todo{Confirm the final enclosure's NEMA type rating and that dust ingress from shredding is addressed.}
    \item \textbf{NEMA ICS 1 / ICS 2 (Industrial Control \& Systems):} contactor and control-device selection and marking follow NEMA control conventions; the Mitsubishi SD-N35 contactor is sized above the motor FLA for the AC-3 (motor) duty.
    \item \textbf{NEMA MG 1 (Motors and Generators):} used to interpret the GE motor nameplate (voltage connection, poles, RPM, service factor) when programming the VFD motor parameters (\texttt{PD141--PD144}).
\end{itemize}

\subsection{Machine-Safety Standards (ISO / IEC)}
\begin{itemize}
    \item \textbf{ISO 12100:} risk-assessment framework that identifies the shredder's primary hazards (rotating blades, entanglement, electrical) and drives the layered safeguards.
    \item \textbf{ISO 13849-1:} the E-stop / lid-interlock / two-hand chain targets a performance level (PL) commensurate with the assessed risk. \todo{Walk through the PL/category calculation or obtain advisor confirmation that formal SIL/PL verification is out of capstone scope.}
    \item \textbf{ISO 13850:} E-stop implemented as a Category 0 stop (immediate removal of power) with fail-safe NC wiring.
    \item \textbf{ISO 13851:} two-hand deadman control -- both buttons must be actuated within 0.5 s of one another and held continuously to enable the motor.
    \item \textbf{IEC 60204-1:} the international analogue of NFPA 79; used to cross-check stop-category definitions and supply-disconnection requirements.
\end{itemize}

\subsection{Occupational Safety (OSHA)}
\begin{itemize}
    \item \textbf{29 CFR 1910.147 (Lockout/Tagout):} the main supply disconnect is lockable so the machine can be positively isolated for blade-area service and maintenance.
    \item \textbf{29 CFR 1910 Subpart S (Electrical):} general electrical-safety practices (guarding of live parts, grounding) observed throughout the panel build.
\end{itemize}

\todo{Before final submission: convert any remaining ``targets / intends to'' language
above into verified compliance statements, attach the panel enclosure datasheet, and
resolve the NFPA 79 neutral-switching deviation note.}

\section{Testing and Validation}

\subsection{Signal Chain Tests}
\begin{itemize}
    \item Manual jumper test (FA-FC short): confirmed PLC X5 reads LOW correctly -- wiring intact.
    \item Guaranteed-trip test (\texttt{PD124 = 1}, \texttt{PD125 = 5.0}): VFD trips reliably on motor run, fault relay fires, PLC X5 drops.
    \item Threshold tuning: 150\% (\texttt{PD124 = 150}) chosen for production based on no-load current (0.5 A) versus expected jam current (above 11 A actual).
\end{itemize}

\subsection{Load Testing}
\todo{Schedule load testing with actual plastic samples once mechanical integration complete. Need ME team coordination.}

\subsection{Safety Validation}
\begin{itemize}
    \item E-stop response time: \todo{measure with scope}.
    \item Lid interlock response: \todo{measure}.
    \item Two-hand control timing: \todo{verify both buttons must be held continuously, simultaneous release stops within X ms}.
\end{itemize}

\section{Results}

\subsection{What Works}
\begin{itemize}
    \item All motor parameters programmed and verified.
    \item Over-torque detection chain validated (VFD detects, relay fires, PLC reads, ladder reacts).
    \item Fail-safe NC wiring confirmed -- system correctly enters fault state on signal chain failure.
    \item HMI communicates with PLC over Ethernet.
\end{itemize}

\subsection{Open Issues}
\begin{itemize}
    \item Vendor-specific Huanyang firmware quirk: \texttt{PD052 = 12} does not fire relay in continue-running mode. Working around with \texttt{PD052 = 02} + \texttt{PD123 = 3}.
    \item PLC ladder logic not fully complete -- state machine implemented, but unjam routine timing needs tuning with real loaded motor.
    \item Mechanical integration pending -- have not yet tested under real shredding load.
\end{itemize}

\question{How much detail should we include about the Huanyang firmware quirk? It is an interesting design lesson (vendor lock-in, never trust the datasheet completely) but distracts from the high-level results.}

\section{Discussion}

\subsection{Design Tradeoffs}
\begin{itemize}
    \item Cost versus reliability: chose Huanyang VFD (\$150) over ATO (\$450). Firmware quirks documented in this report (the Software Design note and Appendix D) for future maintenance.
    \item 110V single-phase versus 220V split-phase mains: 110V chosen for receptacle availability in PSU lab; trade-off is double the input current and need for a dedicated 30 A circuit.
    \item NC fail-safe versus NO active-high jam signal: chose NC for safety; trade-off is potential nuisance lockouts from broken wires (acceptable for shredder).
\end{itemize}

\subsection{Lessons Learned}
\begin{itemize}
    \item Always verify VFD relay function with multimeter before assuming firmware works as documented.
    \item Document deviations from datasheet behavior in version control so future teams can find them.
    \item Power cycle after parameter changes -- some VFDs require it for save to fully take effect.
    \item Use ferrules on all control wires -- loose strand connections caused multiple debugging hours during commissioning.
\end{itemize}

\subsection{Project Management Notes}
\todo{Add a paragraph on how the team coordinated, what tools we used (GitHub, weekly meetings, etc.), and how schedule slipped or held.}

\section{Future Work}

\begin{itemize}
    \item Wireless monitoring (read-only) -- could expose PLC data via the H2-DM1E's built-in web server or an ESP32 bridge.
    \item Data logging: total runtime, jam events per shift, faults. Useful for predictive maintenance.
    \item Predictive jam detection: train a small model on current waveform shape just before jams to detect them earlier.
    \item Mechanical integration with feed hopper that auto-meters plastic into the blade.
    \item Higher-capacity model: scale to 5--10 HP for higher throughput.
\end{itemize}

\section{Ethics and Design Considerations}

A summary of the ethics and design evaluation follows:

\begin{itemize}
    \item \textbf{Public health and safety:} Yes -- multiple redundant safety interlocks, NFPA 70 / NEMA compliance, hardwired safety chain.
    \item \textbf{Environmental:} Yes -- core project purpose is diverting plastic from landfill.
    \item \textbf{Economic:} Yes -- significant cost savings versus commercial alternatives, careful component selection within budget.
    \item \textbf{Global:} Possibly -- approach is replicable globally, components internationally sourced.
    \item \textbf{Cultural:} No -- industrial machine for B2B use, no culture-specific design.
\end{itemize}

\section{References}

\begin{itemize}
    \item NFPA 70 (2023): National Electrical Code (esp. Articles 110, 250, 310, 409, 430).
    \item NFPA 79 (2024): Electrical Standard for Industrial Machinery.
    \item NEMA 250: Enclosures for Electrical Equipment.
    \item NEMA ICS 1 / ICS 2: Industrial Control and Systems.
    \item NEMA MG 1: Motors and Generators.
    \item UL 508A: Industrial Control Panels.
    \item IEC 60204-1:2016: Safety of Machinery -- Electrical Equipment of Machines.
    \item ISO 12100:2010: Safety of Machinery -- Risk Assessment and Risk Reduction.
    \item ISO 13849-1:2023: Safety-related parts of control systems.
    \item ISO 13850:2015: Emergency Stop Function.
    \item ISO 13851:2019: Two-hand control devices.
    \item OSHA 29 CFR 1910.147: The Control of Hazardous Energy (Lockout/Tagout).
    \item Huanyang HY-series VFD User Manual.
    \item AutomationDirect DL205 / Do-more User Manual.
    \item GE 5KE Frame 182T Motor Datasheet.
\end{itemize}

\todo{Add full reference list with URLs / publication info before final.}

\section{Appendices}

\subsection{Appendix A: Bill of Materials}
Major purchased items for the electrical system (procurement BOM, rev 02/20/26):

\renewcommand{\arraystretch}{1.25}
\noindent\begin{tabularx}{\textwidth}{@{}l X l c@{}}
\toprule
\textbf{Item} & \textbf{Description} & \textbf{Mfr. P/N} & \textbf{Critical} \\
\midrule
Motor & AC induction motor, 145TC frame, 3-phase TEFC & PE145TC-2-4 & Yes \\
VFD & Huanyang 1-phase in / 3-phase out drive, 3 HP & HY02D211B-T & Yes \\
HMI & C-More Micro-Graphic 4" color touch panel & EA1-T4CL & Yes \\
Circuit breaker & DIN-rail branch breaker & NBE7 & No \\
Power switch & Single-phase ON/OFF disconnect, 120--230 V & 71008 & No \\
Status lights & Red / green panel indicators & Ichor-provided & No \\
E-stop & Mushroom emergency-stop pushbutton & Ichor-provided & Yes \\
\bottomrule
\end{tabularx}
\renewcommand{\arraystretch}{1.0}

\note{The procurement BOM lists motor \texttt{PE145TC-2-4}; the as-built control
design in this report is parameterized for a GE 5KE182BC205B (3 HP, 230 V, 7.6 A,
4-pole, 1750 RPM). Reconcile the motor line item against the installed motor before
final. Additional control-panel hardware (PLC rack/modules, Mean Well NDR-480-24 PSU,
SD-N35 contactor, Phoenix Contact breaker, brake resistor, illuminated pushbuttons,
fuses) is itemized in the component tables of the Hardware Design section and the
point list in Appendix B.}

\subsection{Appendix B: PLC I/O Point List}
As-built I/O assignments for the DirectLOGIC 205 (D2-09B-1) base.

\textbf{Rack slot layout}
\renewcommand{\arraystretch}{1.2}
\noindent\begin{tabularx}{\textwidth}{@{}l l X@{}}
\toprule
\textbf{Slot} & \textbf{Module} & \textbf{Function} \\
\midrule
1 & H2-DM1E & CPU with built-in Ethernet; serial COM port to HMI \\
2 & D2-08ND3 & 8-ch discrete input, 24 VDC sourcing (X0--X7) \\
3 & F2-08AD-1 & 8-ch analog current input; CH1 = VFD VO motor-current monitor \\
4 & F2-04RTD & 4-ch RTD input (all spare) \\
5 & D2-08TR & 8-ch relay output, sinking, common to PSU $-$V (Y0--Y7) \\
6 & F2-08DA-2 & 8-ch analog voltage output; CH1 (+V1) = VFD VI speed reference \\
7--9 & D2-Fill & Fill panels (reserved) \\
\bottomrule
\end{tabularx}

\vspace{4pt}
\textbf{Discrete inputs (D2-08ND3, sourcing; common to PSU $-$V)}
\noindent\begin{tabularx}{\textwidth}{@{}l X@{}}
\toprule
\textbf{Addr} & \textbf{Field device / function} \\
\midrule
X0 & Forward pushbutton (Autonics S2PR-P3G, NO) \\
X1 & Reverse pushbutton (S2PR-P3Y, NO) \\
X2 & Run 1 / Deadman 1 (S2PR-P3B, NO) \\
X3 & Run 2 / Deadman 2 (S2PR-P3B, NO) \\
X4 & E-stop monitor tap (E22B1 NC, in series with SD-N35 coil A1) \\
X5 & VFD fault relay (FA--FC, NO active-high; HIGH on trip) \\
X6 & Reserved -- Reset pushbutton (S2PR-P3R, planned, unwired) \\
X7 & Spare \\
\bottomrule
\end{tabularx}

\vspace{4pt}
\textbf{Relay outputs (D2-08TR, sinking; common to PSU $-$V)}
\noindent\begin{tabularx}{\textwidth}{@{}l X@{}}
\toprule
\textbf{Addr} & \textbf{Load} \\
\midrule
Y0 & Forward indicator LED (SA-LDG green) \\
Y1 & Reverse indicator LED (SA-LDY yellow) \\
Y2 & Run 1 / Deadman 1 LED (SA-LDB blue) \\
Y3 & Run 2 / Deadman 2 LED (SA-LDB blue) \\
Y4 & Error / fault indicator (Wamco 525, 28 VDC) \\
Y5 & VFD RST (fault-reset pulse, $\sim$500 ms) \\
Y6 & VFD FOR (forward run command) \\
Y7 & VFD REV (reverse run command) \\
\bottomrule
\end{tabularx}

\vspace{4pt}
\textbf{Analog and communications}
\noindent\begin{tabularx}{\textwidth}{@{}l X@{}}
\toprule
\textbf{Point} & \textbf{Connection} \\
\midrule
F2-08AD-1 CH1+ & VFD VO terminal -- motor-current monitor (0--10 V, PD054=1) \\
F2-08DA-2 +V1 & VFD VI terminal -- speed reference (0--10 V, PD002=1) \\
CPU serial COM & EA1-T4CL HMI (operator commands / status \& data) \\
HMI power & Mean Well NDR-480-24 (+V / $-$V), 24 VDC \\
\bottomrule
\end{tabularx}

\vspace{4pt}
\textbf{VFD terminals (Huanyang HY02D211B-T)}
\noindent\begin{tabularx}{\textwidth}{@{}l X@{}}
\toprule
\textbf{Terminal} & \textbf{Connection} \\
\midrule
R & AC hot via main disconnect + 30 A C-curve breaker \\
T & AC neutral via Phoenix Contact TMC 8 3C 15A breaker + SD-N35 contactor pole (as-built: neutral switched -- see NEC note) \\
U / V / W & Motor T1/T2/T3 via colored banana sockets (blue/white/red) \\
P+ / PR & Brake resistor (ATO APCS-300R30-AD, 300 W, 30 $\Omega$) \\
VI / VO & PLC F2-08DA-2 +V1 / PLC F2-08AD-1 CH1+ \\
FOR / REV / RST & PLC D2-08TR Y6 / Y7 / Y5 (sinking, pulled to DCM) \\
FA / FC & PSU +V / PLC X5 (fault relay, PD052=02; FB unused) \\
DCM / ACM & PSU $-$V (shared digital / analog 0 V reference) \\
\bottomrule
\end{tabularx}
\renewcommand{\arraystretch}{1.0}

\subsection{Appendix C: Wiring Diagrams}
\todo{Insert exported PDFs from AutoCAD: power, VFD/motor, PLC/HMI, power distribution.}

\subsection{Appendix D: VFD Parameter Settings}
Programmed parameters on the Huanyang HY02D211B-T (as-built):

\renewcommand{\arraystretch}{1.2}
\noindent\begin{tabularx}{\textwidth}{@{}l l X@{}}
\toprule
\textbf{Param} & \textbf{Value} & \textbf{Meaning} \\
\midrule
PD002 & 1 & Frequency source = external analog voltage (VI, 0--10 V from PLC) \\
PD052 & 02 & Multi-function relay (FA/FC) = fault indication \\
PD054 & 1 & Analog output VO = output current (0--10 V monitor to PLC) \\
PD123 & 3 & Over-torque action = trip/fault (fires the fault relay) \\
PD124 & 150 & Over-torque detection threshold (\% of rated) \\
PD125 & 3.0 & Over-torque detection time (s) \\
PD141 & 230 & Motor rated voltage (V) \\
PD142 & 7.6 & Motor rated current (A) \\
PD143 & 4 & Motor poles \\
PD144 & 1750 & Motor rated speed (RPM) \\
\bottomrule
\end{tabularx}
\renewcommand{\arraystretch}{1.0}

\textbf{Power / braking wiring:} R = AC hot (30 A breaker); T = AC neutral via SD-N35
contactor; U/V/W to motor via colored banana sockets; P+/PR to a 300 W, 30 $\Omega$
brake resistor (ATO APCS-300R30-AD) to absorb regenerative energy during reversal in
the jam-clear cycle. Control wiring is summarized in Appendix B.

\note{Firmware-specific finding: \texttt{PD052 = 12} (continue-running over-torque
indication) did not fire the relay on our Huanyang revision; the working configuration
is \texttt{PD052 = 02} with \texttt{PD123 = 3} (over-torque self-trips, which fires the
fault relay and is read by the PLC on X5).}

\subsection{Appendix E: Test Plan}
Test Plan v1.0 comprises a top-down power-on walkthrough followed by ten bottom-up
test cases. Each case is exercised against the must/should requirements (M-series).

\renewcommand{\arraystretch}{1.2}
\noindent\begin{tabularx}{\textwidth}{@{}l X@{}}
\toprule
\textbf{ID} & \textbf{Test case} \\
\midrule
Top-down & Power-on walkthrough: AC in $\rightarrow$ PSU $\rightarrow$ PLC boot $\rightarrow$ HMI IDLE/READY \\
BU-01 & AC power input and fuse distribution \\
BU-02 & 24 VDC PSU output (Mean Well NDR-480-24) \\
BU-03 & PLC rack initialization (DirectLOGIC 205) \\
BU-04 & E-stop hardware safety circuit \\
BU-05 & Two-hand start (deadman) safety logic \\
BU-06 & Lid interlock safety input \\
BU-07 & VFD speed command and motor RPM (HY02D211B-T) \\
BU-08 & Overcurrent / overload protection \\
BU-09 & HMI operator interface (EA1-T4CL C-More Micro-Graphic) \\
BU-10 & Status indicator lights (power / running / fault) \\
\bottomrule
\end{tabularx}
\renewcommand{\arraystretch}{1.0}

Validation results to date are summarized in the Testing and Validation and Results
sections; load testing under real shredding load is pending mechanical integration.

\vfill
\noindent\rule{\textwidth}{0.4pt}
\noindent\textit{End of rough draft. Comments and questions welcome.}
\noindent\rule{\textwidth}{0.4pt}

\end{document}
